Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-10-08 forecast/paper/response-to-reviewers.tex

  In principle,
  we would expect that different weights may alter the conclusions, though
  likely not substantively. Applying a monotone function to $\tau$ only effectively
  changes the quantile of interest, resulting in a mismatch between the coverage you
  tried to get and the coverage WIS is evaluating. Applying the function to $\tau$
  and $(1-\tau)$ results in an asymmetry, penalizing forecasts that miss on one
  side more than on the other.

  $\bullet$ We have added a sentence in the Evaluation Metrics section emphasizing that
  this metric is standard.
\end{resp}

  2. They do not discuss the possible effects of vaccination rates and other
  factors, though this may be one of the areas of localization they propose to
  investigate.

\begin{resp}
  During the period discussed in the main paper, vaccinations had essentially no
  effect. On Dec 31 2020, when the main evaluation period ends,  according to
  CDC data, about 1\% of the population 
  had received 1 dose. That said, we should probably be more specific in the
  paragraph on lines 31--40: our goal is to use very simple models that do not
  account for extra information (vaccinations but also strains of the virus,
  ``super-spreader'' events, etc.).

@@

\section*{Reviewer 2}
\begin{quote}
  \emph{(items numbered by the editor for convenience of reference)}
\end{quote}

\subsection*{Statistical or Methodological Comments:}

1. Is this really a stationary phenomenon? Over the timerange extending from
pre-lockdown to today, it certainly isn't. The method in this paper of
presenting model prediction errors makes it impossible to see this. People in
econometrics look at cumsums of normalized prediction errors. You can see change
points and trends very easily.

\begin{resp}
  There is little reason to believe that this data is stationary. The models
  however are trained and evaluated over reasonably short periods (2--3 months),
  over which time the behavior may well be stationary.

  $\bullet$ We have added a section
  to the appendix that uses the cumulative sum normalized by baseline as
  suggested. With some exceptions at the beginning of 
  the evaluation period, the relative ordering remains fairly consistent. The AR
  model is easily the worst.

@@

\begin{resp}
  Fixed. Thank you for catching this.
\end{resp}

\subsection*{General Comments: }

8. In my understanding there are some standard models which have been relied
upon I guess millions of times during the pandemic. For example IHME's model.
The authors say a sentence or so about their choice of baseline, saying what
seems to me quite vague about the relation between their baseline and the
heavily used existing models. Wouldn't it be better to identify a specific
widely-used model explicitly as a baseline and then develop measures of
improvement over that specific widely used model? Also, might the authors
explain how the improvements observed by the authors stack up in terms of
concrete differences over the widely used models that people have been using.
Are there major misses that have taken place and could have been avoided?

\begin{resp}
  We have tried to focus mainly on simple time series models in this paper
  rather than comparing to other more elaborate models. A careful
  (out-of-sample) comparison of forecasting performance for state-of-the-art
  models can be found in reference 7 (Cramer et al.). That paper focuses on
  forecasting deaths rather than cases and at the state-level rather than
  disaggregated HRRs. However, their ranking (Figure 2 of Cramer et al.) puts the
  ``COVIDhub-Baseline'' about 10th out of 27 models. As we discuss in the
  manuscript, that baseline is  
  the
  same as the baseline we use for forecasting in this paper: it propagates today
  forward and resamples the residuals to create quantiles (we have expanded the
  description on page 6 to be more explicit). All our ``simplistic'' models beat
  this baseline (the AR(3) does as well). For comparison, IHME (along with 17 other
  ``state-of-the-art'' models) does not. We would argue that using any of the
  models in this paper would be preferable to relying on many of the
  ``widely-used'' models if the goal is forecast accuracy.

@@

  $\bullet$ We have added a sentence to the introduction (around line 40) that
  describes the performance of simple models relative to widely-used models as
  shown in Cramer et al.

  $\bullet$ We have expanded our description of our baseline model (around line
  457). In particular, we emphasize that it is the same as that used by the
  COVID-19 Forecast Hub.

  $\bullet$ To directly address the Reviewer's point about IHME, we include two
  figures here
  that compare our forecasts with state-of-the-art forecasts
  submitted to the COVID-19 Forecast Hub. The first overlays the
  scores from the submissions on top of Figure 3 from the manuscript. We should
  note that the submitted forecasts are at the state level, while ours are at
  the HRR level, but once scaled by the baseline, should be roughly comparable.
  (Note also, these are for cases, not deaths as described in the previous
  bullet.) 
  Only those forecasters that submitted at least 300 forecasts (roughly 50
  states over 6 weeks during the 6 months examined) are shown. From this Figure
  it is clear that all of the forecasters considered in this paper beat most
  submissions. In the second figure, we use the Geometric Mean scaled by the
  baseline as shown in Figure S6 in the Supplement. By this metric, the methods employed in this
  paper would rank in the top 2 of all submitted forecasts, beating the
  COVIDhub-ensemble at all forecast 
  horizons. The improvement of the best indicator assisted model over the AR model
  is roughly the same as the improvement of the AR model over the
  COVIDhub-ensemble.

### 2021-10-09 forecast/paper/supplement-text.tex
revised forecast paper

@@

Following the suggestion of an anonymous reviewer, we investigate two
disaggregated versions of the main forecasting result shown in Figure 3 on the
manuscript. The first (Figure \ref{fig:cumulative-mean}) displays the cumulative
error (summed over all horizons) of each forecaster divided by the cumulative
error of the baseline.  This perspective should illustrate how the models
perform over time, drawing attention to any nonstationary behavior.  During the
initial increase in cases in July 2020, CTIS-CLIIC and Google-AA gain a lot
relative to the AR model. All the indicators do much better than the AR model
during the following downturn (the ebb of the second wave). The AR model
actually improves over the indicators in October 2020, before losing a bit in
late November.

@@

% \section{Comparisons to state-of-the-art forecasters}

% Since mid-July 2020, a number of forecasting teams (48 in total) have submitted
% 1--4 week ahead state-level case forecasts to the COVID19 Forecast Hub
% \cite{ForecastHub}. To compare those forecasts to those created in this paper,
% we selected only those forecasters who submitted at least 300 forecasts for the
% 2-week-ahead target before
% January 1, 2021 (approximately 1 forecast for each state for 6 weeks). This left
% 32 forecasters, one of which, the COVIDhub-4-week-ensemble, was an exact
% duplicate of another. To make the comparison fair, we scaled by the
% COVIDhub-baseline as in Figure 3 of the manuscript. Figure
% \ref{fig:compare-to-hub-mean} shows all submitted forecasts (available 7, 14,
% and 21 days ahead) overlaid on Figure 3. We have highlighted the
% COVIDhub-ensemble in light blue for comparison. All the models developed in this
% paper beat the baseline, and would rank in the top 8 of 31 submitted forecasts
% over this period.

% A more fair comparison that directly adjusts for spatiotemporal difficulty is to
% use the geometric mean scaled by the baseline. This is the same idea shown in
% \ref{fig:fcast-adjusted}. We have also remade this figure overlaying submitted
% forecasts available on the Forecast Hub. It occasionally happens that a
% submitted forecast achieved a WIS of 0, so in this case we use the WIS$+ 1$
% rather than WIS for all forecasters. The result is shown in
% \ref{fig:compare-to-hub-geomean}. By this metric, the methods employed in this
% paper would rank in the top 2, beating the COVIDhub-ensemble at all forecast
% horizons. The improvement of the best indicator assisted model over the AR model
% is roughly the same as the improvement of the AR model over the COVIDhub-ensemble.

>>>>

It is important to note, that even though some indicators, notably CHNG-COVID 
and CHNG-CLI underperform relative to the AR model during upswings, all models 
dramatically outperform the baseline in such periods. Figure 
\ref{fig:upswing-summary-remake} shows the performance of all forecasters relative
to the null model. All forecasters suffer relative to the baseline during down 
periods, but the AR is the worst. In contrast, all models beat the baseline
during up periods, even CHNG-COVID and CHNG-CLI, though not by quite as much as the
AR does.

@@

Following the suggestion of an anonymous reviewer, we investigate two
other disaggregated versions of the main forecasting result shown in Figure 3 on the
manuscript. The first (Figure \ref{fig:cumulative-mean}) displays the cumulative
error (summed over all horizons) of each forecaster divided by the cumulative
error of the baseline.  This perspective should illustrate how the models
perform over time, drawing attention to any nonstationary behavior.  During the
initial increase in cases in July 2020, CTIS-CLIIC and Google-AA gain a lot
relative to the AR model. All the indicators do much better than the AR model
during the following downturn (the ebb of the second wave). The AR model
actually improves over the indicators in October 2020, before losing a bit in
late November. The second (Figure \ref{fig:cumulative-geo-mean}) repeats this 
analysis but aggregating by Geometric mean as described above and displays a
similar pattern.

@@

### 2021-10-09 forecast/paper/supplement.Rmd
revised forecast paper

```{r data-loading}
actuals <- readRDS(here("data", "confirmed_7dav_incidence_prop.RDS"))
fcasts_honest <- readRDS(here("data", "revised_chng", "results_honest.RDS")) %>%
  process_res_cases(actuals) %>%
  filter(forecaster != "gs_inherit") 
fcasts_finalized <- readRDS(here("data", "results_dishonest.RDS")) %>%
  process_res_cases(actuals) %>%
  filter(forecaster != "gs_inherit")
hotspots_honest <- readRDS(here("data", "revised_chng", "hotspots_honest.RDS")) %>%
  process_res_hotspots() %>%
  filter(forecaster != "gs_inherit")
hotspots_finalized <- readRDS(here("data", "hotspots_dishonest.RDS")) %>%
  process_res_hotspots() %>%
  filter(forecaster != "gs_inherit")
cases7dav <- readRDS(here("data", "confirmed_7dav_incidence_num.RDS")) %>%
  rename(case_num = value)
if (params$fd_casefloor >= 0) {
  fcasts_honest <- filter_case_floor(fcasts_honest, cases7dav, params)
  fcasts_finalized <- filter_case_floor(fcasts_finalized, cases7dav, params)
}
if (params$flag_jumps > 0) {
  fcasts_honest <- filter_jumps(fcasts_honest, actuals, params)
  fcasts_finalized <- filter_jumps(fcasts_finalized, actuals, params)
  hotspots_honest <- filter_jumps(hotspots_honest, actuals, params)
  hotspots_finalized <- filter_jumps(hotspots_finalized, actuals, params)
}
```

@@

```{r bootstrap-loading}
fcasts_booted <- readRDS(
  here("data", "results_honest_bootstrapped.RDS")) %>%
  process_res_cases(actuals) %>%
  filter(forecaster != "gs_inherit")
if (params$fd_casefloor >= 0) {
  fcasts_booted <- filter_case_floor(fcasts_booted, cases7dav, params)
}
hotspots_booted <- readRDS(here("data", "revised_chng", "hotspots_honest_bootstrapped.RDS")) %>%
  process_res_hotspots() %>%
  filter(forecaster != "gs_inherit")
if (params$flag_jumps > 0) {
  hotspots_booted <- filter_jumps(hotspots_booted, actuals, params)
  fcasts_booted <- filter_jumps(fcasts_booted, actuals, params)
}
fcasts_booted <- filter(fcasts_booted, forecaster != "gs_subset") %>%
  mutate(forecaster = recode(forecaster, gs = "Google-AA"))
hotspots_booted <- intersect_averagers( # Deal with DV NaN's
  hotspots_booted %>% 
    filter(! is.na(value), !is.na(actual), forecaster != "gs_subset"), 
  "forecaster", 
  c("geo_value", "ahead", "forecast_date", "target_end_date")) %>%
  mutate(forecaster = recode(forecaster, gs = "Google-AA"))
```

@@

```{r up-down-processing}
preds <- readRDS(here("data", "revised_chng", "predictions_honest.RDS"))
preds <- preds %>% 
  filter(abs(quantile - 0.5) < 1e-6) %>% 
  select(-quantile) %>%
  mutate(forecaster = recode(forecaster,
                             AR3 = "AR",
                             AR3CHCLI3 = "CHNG-CLI",
                             AR3CHCOV3 = "CHNG-COVID",
                             AR3DVCLI3 = "DV-CLI",
                             AR3FBCLI3 = "CTIS-CLIIC",
                             AR3GSSAA3_Subset = "gs_subset",
                             AR3GSSAA3_Zero = "Google-AA",
                             Baseline = "strawman"
  )) %>%
  filter(! forecaster %in% c("gs_subset", "strawman"))

@@

```{r upswing-summary-remake, fig.cap="REMAKE: Percent change in average WIS of the forecaster (AR or indicator assisted) relative to the baseline. All models perform poorly durning down periods, but the indicators help. During flat periods, the indicators improve slightly over the AR. During up periods, all forecasters do much better than the baseline, but only some do as well as AR."}
up_down_df_summary <- inner_join(
  left_join(
    corr_df, 
    fcasts_honest %>% select(ahead, geo_value, forecast_date, strawman_wis)),
  up_down, by = c("geo_value","target_end_date")) %>%
  group_by(forecaster, udf) %>%
  summarise(mean = Mean(wis) / Mean(strawman_wis) - 1)
up_down_df_summary %>%
  ggplot(aes(udf, mean, fill = forecaster)) +
  geom_bar(width = 0.6, position = position_dodge(width=0.6),
           stat = "identity") +
  scale_fill_manual(values = fcast_colors, guide = guide_legend(nrow = 1)) +
  theme_bw() +
  scale_y_continuous(labels = scales::percent_format()) +
  geom_hline(yintercept = 0) +
  ylab("% change in Forecaster WIS\n relative to Baseline") +
  xlab("") +
  theme(legend.position = "bottom", legend.title = element_blank())
```

@@

```{r hotspots-upswing-downswing, fig.cap="Classification and loglikelihood separated into periods of upswing, downswing, and flat cases. Like the analysis of the forecasting task in the main paper (see Figure 7), performance is better during down and flat periods."}
hot_udf <- inner_join(
  hotspots_honest,
  up_down %>% select(geo_value, target_end_date, udf))

@@

```{r hotspots-upswing-downswing-remake, fig.cap="REMAKE: Classification and loglikelihood separated into periods of upswing, downswing, and flat cases. The indicator assisted models always have lower classification error relative to the null classifier, while the AR actually does worse in down and flat periods. In terms of loglikelihood, all forecasters have lower likelihood than the null classifier during up periods. In down and flat periods, the indicators generally improve over the AR, while the are worse during up periods."}
# mycummean <- function(x) {
#   isgood <- ! is.na(x)
#   denom <- cumsum(isgood)
#   x[!isgood] <- 0
#   num <- cumsum(x)
#   y <- num / denom
#   y[is.na(y)] <- .5 # deal with empties at the beginning
#   y
# }
# 
# null_classifier <- readRDS(here("data", 
#                                 "all_signals_wide_as_of_2020-05-18.RDS")) %>%
#   rename(jhu = `value+0:jhu-csse_confirmed_7dav_incidence_prop`) %>%
#   select(geo_value, time_value, jhu) %>%
#   group_by(geo_value) %>%
#   arrange(time_value) %>%
#   mutate(lag_value = lag(jhu, 7),
#          apc = (jhu - lag_value) / lag_value,
#          hot = case_when(
#            apc > .25 & lag_value > 30 ~ 1,
#            apc <= .25 & lag_value > 30 ~ 0),
#          null_class = mycummean(hot))

@@

con_tab <- hot_udf %>% 
  filter(!is.na(actual)) %>%
  mutate(pred = value > cutoff) %>%
  group_by(forecaster, udf) %>%
  summarise(m = (mean(pred != actual) - cutoff) / cutoff,
            err = mean(pred != actual)) %>%
  ungroup()

@@

>>>>

```{r data-loading}
actuals <- readRDS(here("data", "confirmed_7dav_incidence_prop.RDS"))
fcasts_honest <- readRDS(here("data", "results_honest.RDS")) %>%
  process_res_cases(actuals) %>%
  filter(forecaster != "gs_inherit") 
fcasts_finalized <- readRDS(here("data", "results_dishonest.RDS")) %>%
  process_res_cases(actuals) %>%
  filter(forecaster != "gs_inherit")
hotspots_honest <- readRDS(here("data", "hotspots_honest.RDS")) %>%
  process_res_hotspots() %>%
  filter(forecaster != "gs_inherit")
hotspots_finalized <- readRDS(here("data", "hotspots_dishonest.RDS")) %>%
  process_res_hotspots() %>%
  filter(forecaster != "gs_inherit")
cases7dav <- readRDS(here("data", "confirmed_7dav_incidence_num.RDS")) %>%
  rename(case_num = value)
if (params$fd_casefloor >= 0) {
  fcasts_honest <- filter_case_floor(fcasts_honest, cases7dav, params)
  fcasts_finalized <- filter_case_floor(fcasts_finalized, cases7dav, params)
}
if (params$flag_jumps > 0) {
  fcasts_honest <- filter_jumps(fcasts_honest, actuals, params)
  fcasts_finalized <- filter_jumps(fcasts_finalized, actuals, params)
  hotspots_honest <- filter_jumps(hotspots_honest, actuals, params)
  hotspots_finalized <- filter_jumps(hotspots_finalized, actuals, params)
}
```

@@

```{r bootstrap-loading}
fcasts_booted <- readRDS(
  here("data", "results_honest_bootstrapped.RDS")) %>%
  process_res_cases(actuals) %>%
  filter(forecaster != "gs_inherit")
if (params$fd_casefloor >= 0) {
  fcasts_booted <- filter_case_floor(fcasts_booted, cases7dav, params)
}
hotspots_booted <- readRDS(here("data", "hotspots_honest_bootstrapped.RDS")) %>%
  process_res_hotspots() %>%
  filter(forecaster != "gs_inherit")
if (params$flag_jumps > 0) {
  hotspots_booted <- filter_jumps(hotspots_booted, actuals, params)
  fcasts_booted <- filter_jumps(fcasts_booted, actuals, params)
}
fcasts_booted <- filter(fcasts_booted, forecaster != "gs_subset") %>%
  mutate(forecaster = recode(forecaster, gs = "Google-AA"))
hotspots_booted <- intersect_averagers( # Deal with DV NaN's
  hotspots_booted %>% 
    filter(! is.na(value), !is.na(actual), forecaster != "gs_subset"), 
  "forecaster", 
  c("geo_value", "ahead", "forecast_date", "target_end_date")) %>%
  mutate(forecaster = recode(forecaster, gs = "Google-AA"))
```

@@

```{r up-down-processing}
preds <- readRDS(here("data", "predictions_honest.RDS"))
preds <- preds %>% 
  filter(abs(quantile - 0.5) < 1e-6) %>% 
  select(-quantile) %>%
  mutate(forecaster = recode(forecaster,
                             AR3 = "AR",
                             AR3CHCLI3 = "CHNG-CLI",
                             AR3CHCOV3 = "CHNG-COVID",
                             AR3DVCLI3 = "DV-CLI",
                             AR3FBCLI3 = "CTIS-CLIIC",
                             AR3GSSAA3_Subset = "gs_subset",
                             AR3GSSAA3_Zero = "Google-AA",
                             Baseline = "strawman"
  )) %>%
  filter(! forecaster %in% c("gs_subset", "strawman"))

@@

@@

```{r hotspots-upswing-downswing, fig.cap="Classification and loglikelihood separated into periods of upswing, downswing, and flat cases. Like the analysis of the forecasting task in the main paper (see Figure 7), relative performance is better during down and flat periods."}
hot_udf <- inner_join(
  hotspots_honest,
  up_down %>% select(geo_value, target_end_date, udf))

@@

```{r hotspots-upswing-downswing-remake, fig.cap="REMAKE: Classification and loglikelihood separated into periods of upswing, downswing, and flat cases. The indicator assisted models always have lower classification error relative to the null classifier, while the AR actually does worse in down and flat periods. In terms of loglikelihood, all forecasters have lower likelihood than the null classifier during up periods. In down and flat periods, the indicators generally improve over the AR, while the are worse during up periods.", eval=FALSE}
# mycummean <- function(x) {
#   isgood <- ! is.na(x)
#   denom <- cumsum(isgood)
#   x[!isgood] <- 0
#   num <- cumsum(x)
#   y <- num / denom
#   y[is.na(y)] <- .5 # deal with empties at the beginning
#   y
# }
# 
# null_classifier <- readRDS(here("data", 
#                                 "all_signals_wide_as_of_2020-05-18.RDS")) %>%
#   rename(jhu = `value+0:jhu-csse_confirmed_7dav_incidence_prop`) %>%
#   select(geo_value, time_value, jhu) %>%
#   group_by(geo_value) %>%
#   arrange(time_value) %>%
#   mutate(lag_value = lag(jhu, 7),
#          apc = (jhu - lag_value) / lag_value,
#          hot = case_when(
#            apc > .25 & lag_value > 30 ~ 1,
#            apc <= .25 & lag_value > 30 ~ 0),
#          null_class = mycummean(hot))

@@

con_tab <- hot_udf %>% 
  filter(!is.na(actual)) %>%
  mutate(pred = value > .5) %>%
  group_by(forecaster, udf) %>%
  summarise(m = (mean(pred != actual) - cutoff) / cutoff,
            err = mean(pred != actual)) %>%
  ungroup()

@@

```{r upswing-summary-remake, fig.cap="Percent change in average WIS of the forecaster (AR or indicator assisted) relative to the baseline. All models perform poorly durning down periods, but the indicators help. During flat periods, the indicators improve slightly over the AR. During up periods, all forecasters do much better than the baseline, but only some do as well as AR."}
up_down_df_summary <- inner_join(
  left_join(
    corr_df, 
    fcasts_honest %>% select(ahead, geo_value, forecast_date, strawman_wis)),
  up_down, by = c("geo_value","target_end_date")) %>%
  group_by(forecaster, udf) %>%
  summarise(mean = Mean(wis) / Mean(strawman_wis) - 1)
up_down_df_summary %>%
  ggplot(aes(udf, mean, fill = forecaster)) +
  geom_bar(width = 0.6, position = position_dodge(width=0.6),
           stat = "identity") +
  scale_fill_manual(values = fcast_colors, guide = guide_legend(nrow = 1)) +
  theme_bw() +
  scale_y_continuous(labels = scales::percent_format()) +
  geom_hline(yintercept = 0) +
  ylab("% change in Forecaster WIS\n relative to Baseline") +
  xlab("") +
  theme(legend.position = "bottom", legend.title = element_blank())
```

### 2021-10-09 forecast/paper/supplement.tex
Revised figures post CHNG situation
revised forecast paper

\caption{\label{tab:dm-test}$P$-values for a one-sided Diebold-Mariano test for improvement in forecast error. The test is for the null hypothesis of equal performance against the alternative that the indicator assisted model is better.}
\centering
\begin{tabular}[t]{lrrrrr}
\toprule
metric & CHNG-CLI & CHNG-COVID & CTIS-CLIIC & DV-CLI & Google-AA\\
\midrule
Geometric Mean Relative WIS & 0.141 & 0.076 & 0.000 & 0.059 & 0.008\\
Mean Relative WIS & 0.186 & 0.137 & 0.002 & 0.074 & 0.064\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{REMAKE: Percent change in average WIS of the forecaster (AR or indicator assisted) relative to the baseline. All models perform poorly durning down periods, but the indicators help. During flat periods, the indicators improve slightly over the AR. During up periods, all forecasters do much better than the baseline, but only some do as well as AR.}\label{fig:upswing-summary-remake}
\end{figure}

@@

\caption{Classification and loglikelihood separated into periods of upswing, downswing, and flat cases. Like the analysis of the forecasting task in the main paper (see Figure 7), performance is better during down and flat periods.}\label{fig:hotspots-upswing-downswing}
\end{figure}

{\centering \includegraphics[width=\textwidth]{fig/hotspots-upswing-downswing-remake-1}

\caption{REMAKE: Classification and loglikelihood separated into periods of upswing, downswing, and flat cases. The indicator assisted models always have lower classification error relative to the null classifier, while the AR actually does worse in down and flat periods. In terms of loglikelihood, all forecasters have lower likelihood than the null classifier during up periods. In down and flat periods, the indicators generally improve over the AR, while the are worse during up periods.}\label{fig:hotspots-upswing-downswing-remake}
\end{figure}

@@

>>>>

\caption{\label{tab:dm-test}$P$-values for a one-sided Diebold-Mariano test for improvement in forecast error. The test is for the null hypothesis of equal performance against the alternative that the indicator assisted model is better.}
\centering
\begin{tabular}[t]{lrrrrr}
\toprule
metric & CHNG-CLI & CHNG-COVID & CTIS-CLIIC & DV-CLI & Google-AA\\
\midrule
Geometric Mean Relative WIS & 0.116 & 0.067 & 0.000 & 0.059 & 0.008\\
Mean Relative WIS & 0.159 & 0.111 & 0.002 & 0.074 & 0.064\\
\bottomrule
\end{tabular}
\end{table}

@@

@@

\caption{Classification and loglikelihood separated into periods of upswing, downswing, and flat cases. Like the analysis of the forecasting task in the main paper (see Figure 7), relative performance is better during down and flat periods.}\label{fig:hotspots-upswing-downswing}
\end{figure}

@@

\caption{Percent change in average WIS of the forecaster (AR or indicator assisted) relative to the baseline. All models perform poorly durning down periods, but the indicators help. During flat periods, the indicators improve slightly over the AR. During up periods, all forecasters do much better than the baseline, but only some do as well as AR.}\label{fig:upswing-summary-remake}
\end{figure}
